Epistemic Semantics in Guarded String Models

### 2020-06-16 tex/draft.tex
Latex macros syntax.tex, and bib file fs.bib

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

@@

\begin{document}
\maketitle
\begin{abstract}
  Constructive and computable multi-agent epistemic possible worlds
  models are defined, where possible worlds models are guarded string
  models in an epistemic extension of Kleene Algebra with Tests.  The
  account is framed as a formal language Epik (Epistemic KAT) for
  defining such models.  The language is interpreted by translation
  into the finite state calculus, and alternatively by modeling
  propositions as lazy lists. The syntax-semantics interface for
  a fragment of English is defined by a categorial grammar.
\end{abstract}

@@

\begin{example}   \label{lexicon1}
{\em Lexicon (partial)}

\hspace{-10mm}\begin{tabular}[t]{l|c|c}
Amy & $e$ & ${R}_a$\\
Bob & $e$ & ${R}_b$\\
it & $d$ & $d$ \\
heads & $d \backslash_D t$ & $\lambda x.0^c{\cdot}h$ \\
tails & $d \backslash_D t$ & $\lambda x.0^c{\cdot}!h$ \\
is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P.\lambda x.P x$ \\
knows & $(e \backslash t)\slash_M t$ &  $\lambda p.\lambda R. {\Diamond}R p$\\
that  & \multicolumn{2}{l}{$(((e \backslash t)\slash_M t) \backslash (e \backslash t)) \slash t$} \\
& \multicolumn{2}{l}{$\lambda p.\lambda m.\lambda R.{\sim}(m ({\sim}p) R)$} \\
whether  & \multicolumn{2}{l}{$(((e \backslash t)\slash_M t) \backslash (e \backslash t)) \slash t$} \\
& \multicolumn{2}{l}{$\lambda p.\lambda m.\lambda R.{\sim}(m ({\sim}p) R)$} \\
& \multicolumn{2}{r}{$+ {\sim}(m p R)$} \\
\end{tabular}
\end{example}

@@

>>>>

% Uncomment this line for the final submission
% Or comment it for the submission version with line numbers.
\aclfinalcopy 
%\def\aclpaperid{***} %  Enter the acl Paper ID here

% CHECK THE BIB STYLE FOR THE STARSEM SUBMISSION

@@

\author{Eric Campbell \\
  Cornell University\\
  \texttt{ehc86@cornell.edu} \\\And
  Mats Rooth \\
  Cornell University\\
  \texttt{mr249@cornell.edu} \\}

@@

\begin{document}
\maketitle
\begin{abstract}
  Constructive and computable multi-agent epistemic possible worlds
  models are defined, where possible worlds models are guarded string
  models in an epistemic extension of Kleene Algebra with Tests.  The
  account is framed as a formal language Epik (Epistemic KAT) for
  defining such models.  The language is interpreted by translation
  into the finite state calculus, and alternatively by modeling
  propositions as lazy lists in Haskell. The syntax-semantics interface for
  a fragment of English is defined by a categorial grammar.
\end{abstract}

\nocite{beesley2003finite,hulden2009foma}
\nocite{karttunen2010update}

@@

\begin{figure}  
\begin{tabular}[t]{l|c|c}
Amy & $e$ & ${R}_a$\\
Bob & $e$ & ${R}_b$\\
it & $d$ & $d$ \\
heads & $d \backslash_D t$ & $\lambda x.0^c{\cdot}h$ \\
tails & $d \backslash_D t$ & $\lambda x.0^c{\cdot}!h$ \\
is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P.\lambda x.P x$ \\
knows & $(e \backslash t)\slash_M t$ &  $\lambda p.\lambda R. {\Diamond}R p$\\
that  & \multicolumn{2}{l}{$(((e \backslash t)\slash_M t) \backslash (e \backslash t)) \slash t$} \\
& \multicolumn{2}{l}{$\lambda p.\lambda m.\lambda R.{\sim}(m ({\sim}p) R)$} \\
whether  & \multicolumn{2}{l}{$(((e \backslash t)\slash_M t) \backslash (e \backslash t)) \slash t$} \\
& \multicolumn{2}{l}{$\lambda p.\lambda m.\lambda R.{\sim}(m ({\sim}p) R)$} \\
& \multicolumn{2}{r}{$+ {\sim}(m p R)$} \\
\end{tabular}
\caption{Partial categorial grammar lexicon. The first column has a word form.
  the second column a categorial type, and third column a semantic translation in
a notation that extends the Epik term language with lambds.}
\end{figure}

@@

\pagebreak

\bibliographystyle{chicago}
\bibliography{fs}
